Estimating duration in the presence of misclassification

### 2024-01-25 biology-data.tex
easy edits
Figure of SARS-CoV-2 natural history

\section{Natural history of the disease}

@@

The CIS (Coronavirus Infection Survey) is a longitudinal study on a representative sample of households.
A full description of the study can be found in \textcite[][supplementary materials]{pouwelsCommunity} or the study protocol~\autocite{cisProtocol}.
In brief, households are invited to the study from databases held by the ONS.
The number invited was to satisfy various target number of individuals swabbing per fortnight; relevant to the discussion in this document is that the target increased from 2,500 by the end of May 2020 to 150,000 in October 2020.
Within a household, all individuals aged 2 and over were invited to participate.
Once invited, an enrolment swab would be taken followed by 4 further weekly swabs (giving a total of 5 swabs on days 0, 7, 14, 21, 28 relative to enrolment) after which monthly swabs are taken.

During the period we consider, the total cohort size expands due to the continuous recruitment into the study.
Following this, the number then decreases and stabilises as those recruited to meet the October target transition from weekly onto monthly testing.
See figure \@ref(fig:test-schedules) for further detail.

>>>>

\section{Natural history of the disease} \label{biology-data:sec:natural-history}

\begin{figure}
  \centering\includegraphics[width=\textwidth]{biology-data/natural-history}
  \caption[Natural history of SARS-CoV-2.]{Natural history of SARS-CoV-2. Reproduced from \textcite{puhachSARSCoV2} with permission.}
  \label{biology-data:fig:natural-history}
\end{figure}

@@

The CIS (Coronavirus Infection Survey) is a longitudinal study on a representative sample of households.
Households are invited to the study from databases held by the ONS.
The number invited was to satisfy various target number of individuals swabbing per fortnight.
Within a selected household, all individuals aged 2 and over were invited to participate.
Once invited, an enrolment swab would be taken followed by 4 further weekly swabs (giving a total of 5 swabs on days 0, 7, 14, 21, 28 relative to enrolment) after which monthly swabs are taken.
A full description of the study can be found in \textcite[][supplementary materials]{pouwelsCommunity} or the study protocol~\autocite{cisProtocol}.

During the period we consider, the total cohort size expands due to the continuous recruitment into the study.
Following this, the number then decreases and stabilises as those recruited to meet the October target transition from weekly onto monthly testing.
